Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-08 analysis/paper/paper.Rmd
Remove unused model objects

load(system.file("extdata",
            "m_f1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_f2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_f3.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_g1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_g2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_g3.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_h1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_h2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_h3.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_i1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_i2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_i3.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_j1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_j2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_j3.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_k1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_k2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
```

>>>>

load(system.file("extdata",
            "m_f1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_f2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_g1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_g2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_h1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_h2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

load(system.file("extdata",
            "m_i1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_i2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
```
